SNIK Quiz: Automatic Generation of Multiple Choice Questionnaires about Information Management in Hospitals

### 2022-01-24 quiz.tex
label-definition and definition

\paragraph{definition}
describe definition-b...

\paragraph{label-definition}
describe label-definition...

>>>>

\paragraph{label-definition}
This gives the user a definition and asks for  the correct term. The terms to be considered are chosen from terms, which are positioned within a distance of two vertices in the graph. So, relative semantic similarity can be assumed. This makes the label-definition-approach especially worthwhile when basic knowledge of terms of information management is required.

% set this as second strat to gain constistency to table 5 
\paragraph{definition}
The definition approach focuses on the question of which definition is fitting for a given term. 
To increase the difficulty of the strategy, the distractors are chosen to be at most two vertices away from the edge which represents the correct term, much like in the label-definition-type.
